A Data-Driven Framework for Neural Field Modeling

### 2011-01-12 ltx/first_order_framework/LaTeX_Manuscript.tex
added few words and references for online algorithm

\mike{A further extension of the framework is to allow for the algorithm to learn online. The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected. A filter that designed to be implemented in an online setting, can be used in place of the smoother. Doing this, while sacrificing accuracy, will increase the speed at which the state estimation can be done and decrease the amount of information that would need to be stored. Approaches for online state estimation include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \cite{Sato00,Cappe09} may be used. These algorithms would facilitate dealing with non-stationary responses as well as providing a basis for optimal, model-based control, suggesting novel approaches to therapy. Something something something estimator, something something something online, something something something complete... about updating parameters rather than finding brand new ones, recursive LS estimator \cite{Ljung1999},}

>>>>

\mike{A further extension of the framework is to allow for the algorithm to learn online. The estimation framework that we have presented is inherently a batch algorithm designed to operate after data has been collected. A simple real-time implementation can be achieved using the UKF  and an online recursive  LS estimator \cite{Ljung1999}, more sophisticated approaches include the incremental EM algorithm \cite{Neal1998}, and the stepwise EM \citep{Sato2000,Cappe2009}.}
